Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\ {\footnotesize \textsuperscript{}}

### 2018-10-09 main.tex
Updates from ShareLaTeX
modify

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subfig}
\usepackage{fancyhdr}
\usepackage{lipsum}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\
  {\footnotesize \textsuperscript{}}}

@@

 \author{\IEEEauthorblockN{Dafang Zhao}
 \IEEEauthorblockA{\textit{Graduate School of Information Science} \\
 \textit{Nara Institute of Science and Technology}}
 \\
 \IEEEauthorblockN{ Michiko Inoue}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
 \textit{Nara Institute of Science and Technology}}
 \and
 \IEEEauthorblockN{Fukuhito Ooshita}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
 \textit{Nara Institute of Science and Technology}}}

\maketitle
\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions. This efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses. Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation. Recently, an efficient reconfiguration method of PV panel connection to optimize power generation is proposed. The method first list candidate configurations and applies precise power simulations to the candidates. However, some of candidates might not be realized by given PV panels and the paper does not show any systematic way to identify such a feasibility. In this paper, we propose a very fast algorithm to check the feasibility with high accuracy.
%This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time. This algorithm is very light and suitable for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

\section{Feasibility}\label{feasPro}
As an example, we consider a PV array where nine panels are connected in three strings. We assume that, in this example, this Fast reconfiguration algorithm estimate number of working module on different current candidate for each panel as shown in Table \ref{tab1}. The dot in table in form of a PV module. We set $N_C$ as the meaning of not candidate, set infeasible MPPs as zero. Through the procedure in Fast reconfiguration algorithm and simplify feasibility check, MPPs are presented in matrix below. [C1, C2, C3, C4] indicate 4 MPP candidates.

To execute a power simulation, we need assign panels into different strings to realize a configuration. However, the way to assign panels is not given in \cite{b10} and some configuration candidates are infeasible. 
The definition of feasibility in (\ref{feas}). When a configuration needs working modules in a string (\textit{$M_S$}) are less than number of working module per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible. 
\begin{equation}
\left\{\begin{matrix}
M_S < Q_{M_{n}} & & \text{Infeasible}\\ 
M_S \geqslant Q_{M_{n}} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}
For an configuration example [C2] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string. According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings. 
Of course we can compute it by using an exhaustive search. However, it is time-consuming. So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.

@@

%First, we summarize the input and output of our algorithm. 
The input of our algorithm is information of a PV array and a configuration. The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate. Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
\begin{table}[htbp]
  \begin{center}
    %% \binom{\begin{pmatrix}
    \begin{tabular}[]{ccccccccccc}
 $\frac{Current\ \rightarrow }{Number\ of\ modules\ \downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\  \\ \hline \hline
$\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\
$\geq 2$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  \\
$\geq 3$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  &$N_C$  &0      &0 \\
$\geq 4$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  & C4    &0      &0 \\
$\geq 5$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &C3     &0      &0      &0  \\
$\geq 6$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &0      &0      &0      &0 \\
$\geq 7$ &$N_C$  &$N_C$  &0      &C2     &0     &0      &0      &0      &0      &0 \\
$\geq 8$ &$N_C$  &C1     &0      &0      &0     &0      &0      &0      &0      &0
    \end{tabular}\label{mppcandidates}
    \end{center}
\end{table}

@@

To assign panels in the right string, following steps are required:
\begin{enumerate} [(1)]
\item Select panels in Panel Selection Order Table. The detail explanation are described next paragraph.\label{step1}
\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following several priorities.
  %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.
  \label{replace}
  %% \subitem  Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
  %% \subitem Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
  %% \subitem Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
\end{enumerate}
\vspace{5.7cm}

\newpage
We explain step (\ref{step1}) that determine the assignment of the $h$-th string. To do this, we consider the number of working modules of each panel for currents less than $i_{s-1}$. Let $m_p(i)$ be the number of working modules of Panel $p$ that work in current $i$. For each panel $p$, we consider the difference vector $D_p=(m_p(i_{s-2})-m_p(i_{s-1}), m_p(i_{s-3})-m_p(i_{s-2}), \ldots, m_p(i_0)-m_p(1))$. The first element $d_1$ of $D_p$ means, if we use panel $p$ in current $i_{s-1}$, we lose $d_1$ working modules in current $i_{s-2}$. Then we sort panels in lexicographic order by vector $D_p$. This means, a panel with minimum module losses should firstly assign to the string with the highest current.
%... Sorry, I didn't complete this comment.
%\vspace{1cm}
%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}. MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively. Additional, number of real working module at MPP current candidates are given in (\ref{e3}). Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
%\begin{equation}
%\begin{aligned}
%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
%\end{aligned}
%\end{equation}
% In order to give more precise reconfiguration strategy. Our proposed algorithm firstly sort panels in a particular order for MPP candidates. For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number. Element in the matrix corresponding to number of module which be able to working on string current.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subfig}
\usepackage{fancyhdr}
\usepackage{lipsum}
\usepackage{stfloats}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\
  {\footnotesize \textsuperscript{}}}

@@

 \author{\IEEEauthorblockN{Dafantg Zhao}
 \IEEEauthorblockA{\textit{Graduate School of Information Science} \\
 \textit{Nara Institute of Science and Technology}}
 \\
 \IEEEauthorblockN{ Michiko Inoue}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
 \textit{Nara Institute of Science and Technology}}
 \and
 \IEEEauthorblockN{Fukuhito Ooshita}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
 \textit{Nara Institute of Science and Technology}}}

\maketitle
\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions. These efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses. Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation. Recently, an efficient reconfiguration method of PV panel connection to optimize power generation is proposed. The method first list candidate configurations and applies precise power simulations to the candidates. However, some of candidates might not be realized by given PV panels and the paper does not show any systematic way to identify such a feasibility. In this paper, we propose a very fast algorithm to check the feasibility with high accuracy.
%This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time. This algorithm is very light and suitable for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

\section{Feasibility}\label{feasPro}
To execute a power simulation, we need assign panels into different strings to realize a configuration. However, the way to assign panels is not given in \cite{b10} and some configuration candidates are infeasible. 
The definition of feasibility in (\ref{feas}). When a configuration needs working modules in \textit{h}-th string (\textit{$M_{Sh}$}) are less than number of working modules per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible. 
\begin{equation}
\left\{\begin{matrix}
M_S < Q_{M_{n}} & & \text{Infeasible}\\ 
M_S \geqslant Q_{M_{n}} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}

As an example, we consider a PV array where nine panels are connected in three strings. We assume that, in this example, this Fast reconfiguration algorithm estimate number of working module on different current candidate for each panel as shown in Table \ref{tab1}. The dot in the table in form of a PV module. We set $N_C$ as the meaning of not configuration candidate and infeasible MPPs are set as zero. Through the procedure in Fast reconfiguration algorithm and simplify feasibility check, MPPs are presented in Table \ref{mppcandidates}. [C1, C2, C3, C4] indicate 4 MPP candidates.

For an configuration example [C1] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string. According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings. So this configuration is infeasible.
Of course we can compute it by using an exhaustive search. However, it is time-consuming. So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.

\begin{table*}[bp]
\caption{Maximum Power Point Candidates}
  \begin{center}
    %% \binom{\begin{pmatrix}
    \begin{tabular}[]{ccccccccccc}
 $\frac{Current\ \rightarrow }{Number\ of\ modules\ \downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\  \\ \hline \hline
$\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\
$\geq 2$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  \\
$\geq 3$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  &$N_C$  &0      &0 \\
$\geq 4$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  & C4    &0      &0 \\
$\geq 5$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &C3     &0      &0      &0  \\
$\geq 6$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &0      &0      &0      &0 \\
$\geq 7$ &$N_C$  &$N_C$  &0      &C2     &0     &0      &0      &0      &0      &0 \\
$\geq 8$ &$N_C$  &C1     &0      &0      &0     &0      &0      &0      &0      &0
    \end{tabular}\label{mppcandidates}
    \end{center}
\end{table*}

@@

%First, we summarize the input and output of our algorithm. 
The input of our algorithm is information of a PV array and a configuration. The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate. Table \ref{mpp3-1} shows the information of a PV panel be given dataset in Table \ref{tab1}.

@@

To assign panels in the right string, following steps are required:
\begin{enumerate} [(1)]
\item Select panels in Panel Selection Order Table. The detail explanation are described next paragraph.\label{step1}
\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following several priorities.
  %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.
  \label{replace}
  %% \subitem  Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
  %% \subitem Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
  %% \subitem Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
\end{enumerate}

We explain step (\ref{step1}) that determine the assignment of the $h$-th string. To do this, we consider the number of working modules of each panel for currents less than $i_{s-1}$. Let $m_p(i)$ be the number of working modules of Panel $p$ that work in current $i$. For each panel $p$, we consider the difference vector $D_p=(m_p(i_{s-2})-m_p(i_{s-1}), m_p(i_{s-3})-m_p(i_{s-2}), \ldots, m_p(i_0)-m_p(1))$. The first element $d_1$ of $D_p$ means, if we use panel $p$ in current $i_{s-1}$, we lose $d_1$ working modules in current $i_{s-2}$. Then we sort panels in lexicographic order by vector $D_p$. This means, a panel with minimum module losses should firstly assign to the string with the highest current.
%... Sorry, I didn't complete this comment.
%\vspace{1cm}
%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}. MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively. Additional, number of real working module at MPP current candidates are given in (\ref{e3}). Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
%\begin{equation}
%\begin{aligned}
%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
%\end{aligned}
%\end{equation}
% In order to give more precise reconfiguration strategy. Our proposed algorithm firstly sort panels in a particular order for MPP candidates. For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number. Element in the matrix corresponding to number of module which be able to working on string current.
